---
title: "Regression and Other Stories: Ch 1.4 - 1.6"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) 
library(rstanarm)
set.seed(08252020)
```


### Building, interpreting, and checking regression models

The authors present four cycles for an iterative data analysis process:

\vfill

1. Model Building: 

\vfill

2. Model Fitting: 

\vfill

3. Understanding model fits: 

\vfill

4. Criticism: 

\vfill

## Classical and Bayesian Inference

Model fitting can be done in different ways... With any approach there are three considerations:

\vfill


\vfill



\vfill



\vfill

\newpage

#### Information

Information pertains to what 

\vfill

#### Assumptions

The authors discuss three basic assumptions that underlay a regression model


\vfill


\vfill


\vfill



\vfill

#### Interpretation

\vfill

__Classical (or frequentist) Inference:__ This approach summarize the data 

\vfill

The results and interpretation are based long-run expectations of the methods that are correct on average (unbiased) and confidence intervals that contain the true parameter the appropriate percent of the time (coverage). 

\vfill

Classical methods do tend to be conservative, in that strong statements are not make with _weak_ data. 

\vfill




\newpage

__Bayesian Inference:__ This approach summarize the data 


\vfill

Results and interpretations are probabilistic 


\vfill

Bayesian inference uses additional information which can potentially give more reasonable results (using the prior to regularize the model), 


\vfill




### Computing

Classical methods tend to use least-squares estimation (or maximum likelihood). 

```{r}
beer <- read_csv('http://math.montana.edu/ahoegh/Data/Brazil_cerveja.csv')
lm_beer <- lm(consumed ~ max_tmp, data = beer)
summary(lm_beer)
```

\newpage

The textbook authors (and your instructor), recommend using Bayesian inference for regression. 

\vfill

Furthermore, using Bayesian methods with _weakly informative_ prior information enables stable estimates and simulation based inference, *but also can result (or approximately result) in frequentist solutions.*

\vfill

```{r}
stan_glm(consumed ~ max_tmp, data = beer, refresh = 0) %>% print()
```
